---
title: "joins"
author: "Scout Leonard"
date: "8/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
```


## Warm Ups

```{r}
penguins_clean <- penguins %>% 
  filter(island != "Torgersen") %>% 
  select(-c(year, sex)) %>% 
  mutate(body_mass_kg = body_mass_g / 1000) %>% 
  rename(location = island)
```

```{r}
penguins_clean_2 <- penguins %>% 
  filter(species == "Adelie") %>% 
  drop_na(flipper_length_mm) %>% 
  group_by(sex) %>% 
  summarize(mean_flip = mean(flipper_length_mm),
            sd_flip = sd(flipper_length_mm),
            sample_size = n())
```

## Joins Practice

### Mutating Joins

Do not use data pasta as a replacement for importing data sets! This is a threat to reproducibility. 

```{r}
animals <- tibble::tribble(
  ~location,   ~species,  ~maturity,
   "lagoon",   "bobcat",    "adult",
    "bluff",   "coyote", "juvenile",
    "creek",      "fox",    "adult",
     "oaks", "squirrel", "juvenile",
    "bluff",   "bobcat",    "adult"
  )


sites <- tibble::tribble(
           ~location,      ~full_site_name, ~jurisdiction,
             "beach",       "Goleta Beach",     "SB City",
            "lagoon",        "UCSB Lagoon",        "UCSB",
             "bluff",       "Ellwood Mesa",     "SB City",
              "oaks", "Fremont Campground",        "USFS"
           )

```

**Full Join**

The safest kind of join :)
This is a mutating join. You can tell becasue columns are for matching key elements. 

```{r}
animals_full_join <- full_join(animals, sites, by = "location")
```

**Left Join **

left_join(animals, sites): I would expect 

```{r}
animals_left_join <- left_join(animals, sites, by = "location")
```


**Inner Join **

```{r}
animals_inner_join <- inner_join(animals, sites, by = "location")
```

### Filtering Joins

Does not increase the number of columns. 

**Semi Join**

```{r}
animals_semi_join <- semi_join(animals, sites, by = "location")
```

**Anti-Join**

Order is important! The code keeps observations with a key match from the first dataframe listed in the command. 

```{r}
animals_anti_join <- anti_join(animals, sites, by = "location")

animals_anti_join_2 <- anti_join(sites, animals, by = "location")
```

*You can pipe together joins, but it is confusing! Make sure you know what you're doing at every step.*










